A boundary-integral framework to simulate \\ the viscous erosion of a porous medium

### 2018-04-06 docs/methods/erosion_methods.tex
NM

Naturally, the flow allowed by the medium is connected to the amount of drag the bodies exert. We therefore show in Fig.~\ref{fig:mbodyplots}(c) the total drag exerted by all bodies as it varies in time. In both cases, the drag remains nearly constant throughout much of the simulation and then drops to zero in the final moments. Although all of the bodies are diminishing in size, the rapid increase in $\umax$ leads to the nearly constant drag that is observed.

To remove the effect of increasing flow rate, we show in Fig.~\ref{fig:mbodyplots}(d) the drag normalized by $\umax$. Since both the pressure and viscous drag depend linearly on $\umax$, this normalized quantity, $F_D / (4 \pi \umax)$, is {\em independent} of $\umax$ and therefore isolates how drag depends on the configuration of bodies. In this way, we can interpret $F_D / (4 \pi \umax)$ as the {\em resistance} associated with the porous network. As seen in the figure, the medium's resistance decreases rapidly as its constituents erode. Since the vertical axis is logarithmic, the rate is roughly exponential at early times.

%
The figure shows the resistance to decrease rapidly as the bodies erode. Once again the vertical axis is logarithmic, and so the linear trend corresponds to exponential decay of $F_D / (4 \pi \umax)$. We propose that the channelization is responsible for creating such a rapid decline in the network resistance.

>>>>

Naturally, the flow allowed by the medium is connected to the amount of drag the bodies exert. We therefore show in Fig.~\ref{fig:mbodyplots}(c) the total drag exerted by all bodies as it varies in time. In both cases, the drag remains nearly constant throughout much of the simulation and then drops to zero in the final moments. Although all bodies are diminishing in size, the associated increase in $\umax$ leads to the nearly constant drag that is observed.

To remove the effect of increasing flow rate, we show in Fig.~\ref{fig:mbodyplots}(d) the drag normalized by $\umax$. Since both the pressure and viscous drag depend linearly on $\umax$, this normalized quantity, $F_D / (4 \pi \umax)$, is {\em independent} of $\umax$ and therefore isolates how drag depends on the configuration of bodies. In this way, we can interpret $F_D / (4 \pi \umax)$ as the {\em resistance} associated with the porous network. As seen in the figure, the medium's resistance decreases rapidly as its constituents erode. Since the vertical axis is logarithmic, the rate is roughly exponential at early times. As before, the reduction in area-fraction is not sufficient to explain this rapid decrease, leaving the channelization process as the most likely explanation.
